\Large \bf \sys: Library-Oriented Program Analysis

### 2020-05-27 paper/draft.tex
Update

Dynamic analysis is a type of analysis performed by (and while) executing a program, with the goal of extracting information about the program and its execution.
Such information may include the ability to infer execution invariants, check security constraints, and extract performance characteristics~\cite{analysis:10}.
Contrary to other types of analysis, its key benefits make it the primary (or only) candidate in a variety of scenarios---namely, ones that require:
  (i) current runtime information, such as profiling data, in view of changing load patterns~\cite{staticdynamic},
  (ii) accurate visibility into the execution, devoid of abstraction or approximation~\cite{staticdynamic},
  (iii) Turing-complete policies, where monitors themselves are programs~\cite{contracts1, contracts2, contracts3},
  (iv) dynamic or runtime-reflection features, such as the ones present in Python and JavaScript~\cite{jsanalysis1, jsanalysis2}.

@@

  \item \textbf{Q2} Is it usable?
     We answer this question in \S\ref{impl}, by implementing these and other analyses.
    \sys operates as a library around a unmodified runtime environments, does not require investment in a new language, and leads to analysis expressions that are comparable to conventional frameworks.
    % Analyses expressed in \sys are about 4$\times$ smaller than equivalent analyses written for a heavy-weight instrumentation framework.

  \item \textbf{Q3} How does it perform? We answer this question here.
  For the most libraries, \sys overheads are under 5\%~\sx{meso}.
  \sys is over an order-of-magnitude faster than Jalangi, a state-of-the-art dynamic analysis framework~\sx{meso}.
  By executing on unmodified runtimes, \sys has significantly better compatibility:
    to execute, Jalangi requires significant library modifications~\sx{meso}.
  \sys scales to three large applications with hundreds of libraries while interposing on several thousands of objects~\sx{macro}.
  Most of the overheads come from tracking global variables, but loading-time wrapping and runtime interposition overheads are negligible~\sx{micro}
  % The majority of the overheads come from the use of \ttt{with}, a

@@

We apply \sys on three large applications:
  KoaBlog~\cite{koa}, a minimal blogging platform built on the Koa framework;
  Moeda~\cite{moeda}, a command-line currency converter that, among other features, uses online currency exchange rates; and
  Terminalizer~\cite{terminalizer}, an application for recording terminal sessions to generate animated gif images and shareable web-player links.
These applications are highly popular, with Koa.js and Terminalizer having 28.3K and 8.7K GitHub stars respectively.
Their structural and performance characteristics are shown in Tab.~\ref{tab:macro}.

@@

\heading{Interposition Overheads}
Table~\ref{tab:synthetic} depicts the results of the three analyses applied to a subset of the aforementioned synthetic benchmarks.
The first column indicates the focus of the benchmark; not all analysis--benchmark combinations are useful:
  for example, the ``custom-delay'' benchmark features static bottlenecks across its dependency tree but does not involve interesting access patterns.
\sys-induced slowdown is under 2$\times$, except for the first two cases that feature \emph{only} accesses.
Close inspection confirms a correlation to the number of wrapped objects and the frequency of accesses:
  these benchmarks feature artificially tight loops with high-frequency accesses.
Transformation overheads themselves (not in Tab.~\ref{tab:synthetic}) remain under $1ms$.

@@

There are a few highlights worth noting.
While the number of objects wrapped by\sys starts growing exponentially, it quickly reaches an average upper bound of 400 (depending on the exact benchmark).
Accesses grow quickly for the first couple of levels---objects for some of these libraries are hit several thousand times---but then remain stable.
This is usually because most interfaces follow a mostly-flat format where all methods are defined at the top level or right under.

@@

By operating on library boundaries, \sys uses a few special language features, supported by all major programming languages.
First, \sys needs to re-wire the \ttt{import} keyword:
  if it is a function (\eg JavaScript, Scheme, Racket), re-wiring amounts to an overwrite;
  if it is a special non-functional keyword, re-wiring needs to be prefixed by a rewriting pass replacing \ttt{import} with a function (during module loading).
% This is simplified by the fact that the import syntax is trivial.

It also needs the ability to interpose on values and transform their components.
% This is relatively easy in languages that provide meta-programming capabilities.
Dynamic programming languages offer runtime reflection and conveniently expose object accesses as (over-loadable) functions---\eg \ttt{Proxy} objects in JavaScript, metatables in Lua, metaclasses in Python, and direct-accessor meta-programming Ruby.
Compiled languages would apply transformations with static metaprogramming facilities, traversing and transforming objects at compile time.
Examples include templates and macro expansions such as Haskell's Template and Rust's macro system.
% Other languages, such as Java and Julia, provide both static and dynamic reflection capabilities, allowing considerable freedom in the choice of implementation.
% Fifth, \sys makes extensive use of interposition which is also available in different programming languages.
% Static programming languages provide different types of support for

>>>>

Dynamic analysis is a type of analysis performed by (and while) executing a program, with the goal of extracting information about the program and its execution.
Such information may include the ability to infer execution invariants, check security constraints, and extract performance characteristics~\cite{analysis:10}.
Contrary to other types of analysis, its key benefits make it the primary (or only) candidate in a variety of scenarios---namely, ones that require:
  (i) current runtime information, such as profiling data, in view of changing load patterns~\cite{staticdynamic},
  (ii) accurate visibility into the execution, devoid of imprecision or approximation~\cite{staticdynamic},
  (iii) Turing-complete policies, where monitors themselves are programs~\cite{contracts1, contracts2, contracts3},
  (iv) dynamic or runtime-reflection features, such as the ones present in Python and JavaScript~\cite{jsanalysis1, jsanalysis2}.

@@

  \item \textbf{Q2} Is it usable?
     We answer this question in \S\ref{impl}, by implementing these and other analyses.
    \sys operates as a library around unmodified runtime environments, does not require investment in a new language, and leads to analysis expressions that are comparable to conventional frameworks.
    % Analyses expressed in \sys are about 4$\times$ smaller than equivalent analyses written for a heavy-weight instrumentation framework.

  \item \textbf{Q3} How does it perform? We answer this question here.
  For the most libraries, \sys overheads are under 5\%~\sx{meso}.
  \sys is over an order-of-magnitude faster than Jalangi, a state-of-the-art dynamic analysis framework~\sx{meso}.
  By executing on unmodified runtimes, \sys has significantly better compatibility:
    to execute, Jalangi requires significant library modifications~\sx{meso}.
  \sys scales to three large applications with hundreds of libraries while interposing on several thousands of objects~\sx{macro}.
    Most of the overheads ($>95\%$)come from tracking global variables, but loading-time wrapping and runtime interposition overheads are negligible~\sx{micro}
  % The majority of the overheads come from the use of \ttt{with}, a

@@

We apply \sys on three large applications:
  KoaBlog~\cite{koa}, a minimal blogging platform built on the Koa framework;
  Moeda~\cite{moeda}, a command-line currency converter that, among other features, uses online currency exchange rates; and
  Terminalizer~\cite{terminalizer}, an application for recording terminal sessions to generate animated gif images and shareable web-player links.
These applications are highly popular, with Koa and Terminalizer having 28.3K and 8.7K GitHub stars respectively.
Their structural and performance characteristics are shown in Tab.~\ref{tab:macro}.

@@

\heading{Interposition Overheads}
Table~\ref{tab:synthetic} depicts the results of the three analyses applied to a subset of the aforementioned synthetic benchmarks.
The first column indicates the focus of the benchmark; not all analysis--benchmark combinations are useful:
  for example, the ``custom-delay'' benchmark features static bottlenecks across its dependency tree but does not involve interesting access patterns.
\sys-induced slowdown is under 2$\times$, except for the first two cases that feature \emph{only} accesses.
Close inspection confirms a correlation to the number of wrapped objects and the frequency of accesses:
  these benchmarks feature artificially tight loops with high-frequency accesses.
Transformation overheads themselves (not in Tab.~\ref{tab:synthetic}) remain under 1ms.

@@

There are a few highlights worth noting.
While the number of objects wrapped by \sys starts growing rapidly, it quickly reaches an average upper bound of 400 (depending on the exact benchmark).
Accesses grow exponentially for the first couple of levels---as objects at levels have multiple fields, many of which are accessed several thousand times---but then stabilize around level 5.
This is because most interfaces follow a mostly-flat format where all methods are defined at the top level or right under.

@@

By operating on library boundaries, \sys uses a few special language features supported by all dynamic programming languages.
First, \sys needs to re-wire the \ttt{import} keyword:
  if it is a function (\eg JavaScript, Scheme, Racket), re-wiring amounts to an overwrite;
  if it is a special non-functional keyword, re-wiring needs to be prefixed by a rewriting pass replacing \ttt{import} with a function (during module loading).
% This is simplified by the fact that the import syntax is trivial.

It also needs the ability to interpose on values and transform their components.
% This is relatively easy in languages that provide meta-programming capabilities.
Dynamic programming languages offer runtime reflection and conveniently expose object accesses as (over-loadable) functions---\eg \ttt{Proxy} objects in JavaScript, metatables in Lua, metaclasses in Python, and direct-accessor meta-programming Ruby.
Compiled languages would apply transformations with static metaprogramming facilities, traversing and transforming objects at compile time.
Examples include templates and macro expansions such as Template Haskell and Rust's macro system.
% Other languages, such as Java and Julia, provide both static and dynamic reflection capabilities, allowing considerable freedom in the choice of implementation.
% Fifth, \sys makes extensive use of interposition which is also available in different programming languages.
% Static programming languages provide different types of support for
